The Chemistry Development Kit (CDK). 3. Atom typing, Rendering, Molecular Formula, and Substructure Searching

### 2016-07-23 article.tex
Meta sections

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Competing interests}
XX and YY have companies that sell solutions based on the CDK.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Authors contributions}
    Text for this section \ldots

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Competing interests}
JWM and NJ work for a company that sell solutions based on the CDK.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Authors contributions}
All authors wrote and contributed source code or documentation to the CDK
library. Some authors have peer-reviewed source code for the library.
ELW, JWM, RG, and CS are project leaders. All authors have contributed to the
content of this paper and approved the final version.
